Excuse me, do you have a moment to talk about version control?

### 2017-05-13 README.Rmd
Move 'things you can tackle later'
Mention basic, mission critical config; closes #2

GitHub __issues__ are another powerful feature of the platform. Recall that we are repurposing Git, a tool designed to facilitate software development. The issues for a project are its bug tracker. For projects that are not pure software development, we use this machinery to organize our to do list more generally. The basic unit is an issue and you can interact with them in two ways.

@@

## Initial Git setup

@@

  * Install Git. Depending on your OS, Git might already be installed. But many of us will need to do this.

>>>>

GitHub __issues__ are another powerful feature of the platform. Recall that we are repurposing Git, a tool designed to facilitate software development. The issues for a project are its bug tracker. For projects that are not pure software development, we coopt this machinery to organize our to do list more generally. The basic unit is an issue and you can interact with them in two ways.

@@

## Initial system setup

@@

  * Install Git. Depending on your OS, Git might already be installed. But many of us will need to do this. Some basic configuration is also critical, such as setting your username and email.
